Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-20 rates-neurips-21/rates.tex
introduc

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\paragraph{The surrogate risk framework.}
In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.

@@

\section{Upper bound: polyhedral surrogates}
In this section, we develop the proof of Theorem \ref{thm:main-upper}.
At a high level, the proof has two parts:
\begin{enumerate}
  \item Fix $p \in \simplex$.
        Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
  \item Apply this result to a carefully chosen finite subset of $\simplex$. Argue that the maximum over the $\alpha_p$'s in this finite set gives the constant factor for the transfer rate.
\end{enumerate}
We view both parts as relatively surprising.
The first part will actually hold for any calibrated surrogate.
The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ cover the whole simplex with a finite number of polyhedral level sets.
In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
This is related to embeddings \bo{cite}.

\paragraph{Part 1.}
First, we establish a linear transfer rate for any fixed conditional distribution $p$.
This holds for any calibrated surrogate, not necessarily polyhedral.
\begin{lemma} \label{lemma:fixed-p}
  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
\end{lemma}
\begin{proof}
  Fix $p \in \simplex$.
  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
  By definition of calibration, we have $B_p > 0$.

@@

\paragraph{Part 2.}
Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
However, we know this is false in general: not all surrogates yield linear transfer rates!
Indeed, for many surrogates, the supremum will be $+\infty$.

However, polyhedral surrogates have a special structure that allows us to show $\alpha$ is finite.
We first present several general lemmas, then the key implication from $L$ being polyhedral.
The general results are known \bo{cite}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In supervised learning, our goal is to learn a hypothesis that solves some target problem given labeled data.
This target problem is given by a target loss, which is often discrete in the sense that the prediction lies in a finite set: classes, rankings, etc.
As minimizing target losses over a data set is typically NP-hard, we instead turn to the general paradigm of \emph{surrogate risk minimization}.
Here a surrogate loss function is chosen, and one minimizes the surrogate loss over the data instead of the target.
A link function then maps the surrogate predictions to target predictions.

Naturally, a central question in surrogate risk minimization is how to choose the surrogate loss.
A minimal requirement is statistical \emph{consistency}, which roughly says that approaching the best possible surrogate loss will eventually lead to the best possible target loss.
More generally, we would like to understand the rate at which this minimization occurs, called the \emph{generalization rate}: in terms of the number of data points, how quickly the target loss approaches the best possible.
In other words, if we define the \emph{regret} of a hypothesis $h$ to be its performance relative to the best possible,

Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
We define the \emph{regret}
Informally, a surrogate regret bound takes the form
\begin{equation}
  \label{eq:surrogate-regret-bound-informal}
  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
\end{equation}
where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.

Here regret is the difference between a hypothesis
  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
  We provide two general results.
  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
  The second shows that for ``non-polyhedral'' surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.

\section{Introduction}
\paragraph{The surrogate risk framework.}
In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.

@@

\section{Upper Bound: Polyhedral Surrogates}
In this section, we develop the proof of Theorem \ref{thm:main-upper}.
At a high level, the proof has two parts:
\begin{enumerate}
  \item Fix $p \in \simplex$.
        Prove that there is some constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
      \item Apply this result to each $p$ in a carefully chosen finite subset of $\simplex$.
        Argue that the maximum $\alpha_p$ from this finite set suffices for the slope of the linear transfer function.
\end{enumerate}
\raft{On ``We view both parts as relatively surprising'' I'm not sure the first part is.  I mean, it is to \textbf{us}, but as you point out, in retrospect it follows immediately from the definition...}
The first part will actually hold for any calibrated surrogate.
The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets.
In other words, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected loss.
This observation is related to embeddings \bo{cite}.

\subsection{Part 1: Linear transfer for fixed $p$}
First, we establish a linear transfer rate for any fixed conditional distribution $p$.
This holds for any calibrated surrogate, not necessarily polyhedral.
\begin{lemma} \label{lemma:fixed-p}
  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
\end{lemma}
\begin{proof}
  Fix $p \in \simplex$.
  Let $C_p = \max_{r \in \R} R_{\ell}(r,p)$.
  The maximum exists because $\ell$ is discrete, i.e. $\R$ is finite.
  Meanwhile, recall that, when defining calibration, we let $B_{L,\psi,\ell}(p) = \{R_L(u,p) ~:~ \psi(u) \not\in \gamma(p)\}$.
  Let $B_p = \inf B_{L,\psi,\ell}(p)$.
  By definition of calibration, we have $B_p > 0$.

@@

\subsection{Part 2: Linear overall transfer function}
Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
However, we know this is false in general: not all surrogates yield linear transfer rates!
Indeed, for many surrogates, the supremum will be $+\infty$.

However, polyhedral surrogates have a special structure that allows us to show $\alpha$ is finite.
We first present several general lemmas, then the key implication from $L$ being polyhedral.
The general results are known \bo{cite}\raft{Not sure what this sentence means}.
